Automated Lensing Learner - I: An automated Strong Lensing Identification Pipeline

### 2017-03-14 ms.tex
Final paragraph summarizing neural network use in strong lensing systems

% Image identification works: visual, ``robot'' identification -
% ArcFinder, RingFinder..., and citizen science (space warps).  Many
% of these rely on some explicit aspect of the image's morphology
% (give example), filtering, ... ....  Specifics of the methodology
% how the instrument affects the strong lensing signal, and the
% objects of interest.
Over the last decade, infrastructure for both large scale visual and
automated image classification emerged. By nature, the human eye is
one of the best discriminators for image classification.  Visual arc
identification has been effective through the use of citizen science
platforms.  {\em SpaceWarps} is an example of citizen science based
image classification of strong lensing systems in Canada France Hawaii
Telescope Science (CFHTLS) telescope observations
\citep{marshall_etal16,more_etal16}.  These platforms are quite
successful for a dataset like CFHTLS, classifying \todo{XX in XX
  time}\citep{}.  However, future datasets like Euclid
\citep{oguriandmarshall_10} and LSST \cite{} will be \todo{XX} times
this size, challenging the scalability of a citizen science approach.

@@

% Classical machine learning methods
More recently, these methods have transitioned to using ``machine
learning'' algorithms.  In classical machine learning, we can train a
model to separate a dataset according to some desired classification
scheme.  However, we still need to reduce the dimensionality of the
problem by removing information in the images that do not pertain to
the classifier.

Examples of automated classification will...
% Previous works and our goal to make a universal pipeline 
Machine learning to automate.  Here, we focus on the improvement from
preprocessing the images and describe the pipeline, which is publicly
available.  Depending on the image type, different preprocessing is
likely necessary (rings, multiply lensed quasars, etc.)

% Recent works, deep learning
Much more recent works have made use of neural networks to

\citep{petrillo_etal17} convolutional neural networks with the Kilo
Degree Survey. \citet{bom_etal16} ... \citet{lanusse_etal17} using
state-of-the-art residual networks to....  directly in the image space
with minimal image pre-processing.

% Need to optimize for completeness and purity.  Arc counts and mass
% reconstruction.
In general, lensed image finding must optimize for completeness and
purity.  In the application of arc abundance comparisons with
cosmological predictions, completeness is important; we must be able
to understand the reasons and frequency of false negatives.  In the
application of mass reconstruction of the lensing object, completeness
in strong lensing system identifications will allow us

% Purity issues
Since spectroscopic confirmation of background lensed images is
expensive, purity is key; we must minimize false positives that would
waste follow up telescope time.  We discuss the performance of our
image processing and classification pipeline with respect to the
completeness and purity rates of our trained models and illustrate the
scalability of training our models [wc???].

>>>>

% Image identification works: visual, ``robot'' identification -
% ArcFinder, RingFinder..., and citizen science (space warps).  Many
% of these rely on some explicit aspect of the image's morphology
% (give example), filtering, ... ....  Specifics of the methodology
% how the instrument affects the strong lensing signal, and the
% objects of interest.
Over the last decade, infrastructure for both large scale visual and
automated image classification emerged. By nature, the human eye is
one of the best discriminators for image classification.  Visual arc
identification has been effective through the use of citizen science
platforms.  {\em SpaceWarps} is an example of citizen science based
image classification of strong lensing systems in Canada France Hawaii
Telescope Science (CFHTLS) telescope observations
\citep{marshall_etal16,more_etal16}.  These platforms are quite
successful for a dataset like CFHTLS, classifying \todo{XX in XX
  time}\citep{}.  However, future datasets like Euclid
\citep{oguriandmarshall_10} and LSST \cite{} will be \todo{XX} times
this size, and {\em Euclid} is estimated to find tens of thousands
galaxy-scale strong lenses \citep{pawase_etal12}.  The volume of
upcoming data challenges the scalability of a citizen science
approach.

@@

% Classical machine learning methods
The latter of these methods have transitioned to using ``machine
learning'' algorithms for the pattern recognition step.  In classical
machine learning, we can train a model to separate a dataset according
to some desired classification scheme.  However, we still need to
reduce the dimensionality of the problem with a feature extraction
method.  The dominant ``features'' of that determine image
classification are not a priori known, but determined by the
algorithm.

% Recent works, neural nets, and deep learning
Much more recent works have made use of a subset tool in machine
learning, neural networks, to classify images either from input image
parameters or directly in image space.  In \citet{estrada_etal07},
authors used input shape parameters to train neural nets to identify
arc candidates.  \citet{agnello_etal15} used neural networks trained
on data from multiband magnitudes, and \citet{bom_etal16} used
extracted morphological parameters.

% Convolutional and residual
In image space, \citep{petrillo_etal17} used data from the Kilo Degree
survey to train convolutional neural networks with the Kilo Degree
Survey. \citet{bom_etal16}. \citet{lanusse_etal17} using
state-of-the-art residual networks to....  directly in the image space
with minimal image pre-processing.
